PreProc2

### 2019-11-06 preproc2.Rmd
week 2 bigrams and trigrams

```{r, init}
library(quanteda)
library(readtext)
library(spacyr)
```

@@

# data import
```{r}
dat.twit <- readtext("./en_US.twitter.txt", cache = FALSE)
# summary(corpus(dat.twit), 5)
# or

@@

>>>>

```{r, init, eval=FALSE}
library(quanteda)
library(readtext)
library(spacyr)
library(ggplot2)
library(wordcloud)
```

@@

# data import
```{r, dataimport, cache = TRUE}
dat.twit <- readtext("./en_US.twitter.txt", cache = FALSE)
# summary(corpus(dat.twit), 5)
# or

@@

```{r}
texts(myN)[2]
texts(myN)[4]
texts(myN)[100]
texts(myN)[1000]
```

## Data-Feature Matrix

```{r}
unigram = tokens(myN, remove_numbers = T, remove_punct = T)
ngramTable
```

```{r}
ngram1 <- tokens(myN[1],n=1)
ngramTable <- as.data.frame(table(ngram1))
# count the number of distinct 1-grams, matching Types for BNP text
nrow(ngramTable)
#1125
# count total number of 1-grams (i.e. sum the frequencies), matching Tokens
sum(ngramTable$Freq)
#3280
# print most frequent 1-grams
tail(ngramTable[order(ngramTable$Freq),])
```

data feature matrix

dat.dfm <- dfm(dat, ngrams=ng, toLower = FALSE, removePunct = FALSE, what = "fasterword", verbose = FALSE)
```{r}
dfm.twit = dfm(myN, remove_numbers = T, remove_punct = T)
```

top frequent words

```{r}
topfeatures(dfm.twit, 20)
#dfm without stopwords
dfm.twit = dfm(myN, remove_numbers = T, remove_punct = T,
               remove = stopwords("english"))
top20 = topfeatures(dfm.twit, 20)
topfeatures(dfm.twit, 20)
```

```{r}
top100 = topfeatures(dfm.twit, 100)
topfeatures(dfm.twit, 100)
```

creating a wordcloud
```{r}
library(wordcloud)
set.seed(100)
textplot_wordcloud(dfm.twit, min_count = 3000, random_order = FALSE,
                   rotation = .25,
                   color = RColorBrewer::brewer.pal(8, "Dark2"))
```

```{r}
qplot(y = top20, x = names(top20))
```

bigrams
```{r}
twit.bigram <- tokens(myN[1],n=2, remove_numbers = T, remove_punc = T)
twit.bigram
```

```{r}
dfm.twit.bigram <- dfm(myN, ngrams=2, remove_punct = T, remove_numbers = T, concatenator = " ", remove = stopwords("english"), verbose = T)
dfm.twit.bigram[1:5, 1:5]
```

docfreq function

(weighted) document frequency of a feature.

```{r}
freqs.twit = docfreq(dfm.twit.bigram)
topfeatures(dfm.twit.bigram, 50)
```

trigrams

```{r}
dfm.twit.trigram <- dfm(myN, ngrams=3, remove_punct = T, remove_numbers = T)
dfm.twit.trigram[1:5, 1:5]
```

```{r}
topfeatures(dfm.twit.trigram, 50)
```
